Accurate binding of calcium to phospholipid bilayers by effective inclusion of electronic polarization

### 2017-10-11 Manuscript/manuscript.tex
A dirty paragraph on the difference, when I consider carbonyl more as dipoles, added to stoichiometry section.

>>>>

Internal side-note: 
However, $\Sigma ^\mathrm{Ca^{2+}} _\mathrm{O_{carb.}}$ is increased 
when carbonyl dipoles are scaled only with 0.945 
(roughly done through charge redistribution)
 to : $\Sigma ^\mathrm{Ca^{2+}} _\mathrm{O_{carb.}} \approx 0.08 $.    % = (70.-59.8)/128 . 
This does not change the dominance of phosphates, which still interact more than 6x times more. That's good.
In addition, the probability of states, containing sn-1:O increases from 6\% to 10\%.
The residence times change to 75ns (90\% of bound time) and max is 185ns.
That's not much, too. It certainly is not a game changer, I'd even call it to be within accuracy. 
The slight problem may be that with this tweak, there's approx. 20\%  more cations bound to the membrane,
which means, I'd need to tune the sigma parameter a bit. 
Not $f_q$ -- that's set by the simulations with the surfactant. 
That could detune the membrane structure \dots
I think that's within the accuracy.
